Multiplex stream graphs

### 2019-04-25 tex/main.tex
modification de la définition, ajout de la preuve sur l'union des substreams
ajout de citations dans la def
ajout d'une contrainte dans la def (existence d'au moins une layer à un temps donné)
ajout de la preuve sur l'union

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{a4wide}
\usepackage{amsmath}
\usepackage{todonotes}
\usepackage{xcolor}
\usepackage{amsthm}
\usepackage{amssymb}

@@

	\subsection{Definition}
    We define a multiplex stream graph as a tuple $M = (T,T_M,V,W_M,E_M,{\cal L})$, such that $T$ and $V$ are, respectively, a time interval and a set of nodes, just like for stream graphs \cite{stream}.
    As for multilayer graphs \cite{mlkiv}, ${\cal L}$ is a set of $d$ {\em aspects}; ${\cal L} = \{L_i\}_{i=1}^d$, and an element $\alpha_i$ of $L_i$ is named {\em elementary layer}. An element of $L=L_1\times \dots \times L_d$ is named {\em layer}. From those elements, the set of {\em node-layers } $V_M$ is defined as follows : $V_M = \{ (u,\alpha), u\in V, \alpha \in L\}$.

	$T_M$ is a set of intervals of $T$ so for that each layer $\alpha$, $T_{\alpha}$ is the interval at which the layer exists.

@@

   $E_M \subseteq T\times V_M \otimes V_M$ are the links appearing with respect to time.

@@

	\pimprenelle{FIGURE + EXEMPLE }

	\begin{ex}[Research world]\label{exresearch}
	We consider a set of people working in research.

@@

	The {\em union} of two substreams $S_1$ and $S_2$ is defined as follows :
	\begin{align*}
		S' = S_1 \cup S_2 = (T', V_1 \cup V_2, W_1 \cup W_2, E' \})\\
		T' = [\min(T_1,T_2),\max(T_1,T_2)]\\
		E' = E_1 \cup E_2 \cup (T'\times V_1 \times V_2 \cap E )
	\end{align*}

@@

	\begin{prop}
		\[
			\bigcup_{(\alpha,\beta) \in L^2} S^{(\alpha,\beta)} = S
		\]
	\end{prop}

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{a4wide}
\usepackage{amsmath}
\usepackage{todonotes}
\usepackage{xcolor}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{accents}

@@

	\subsection{Definition}
    We define a multiplex stream graph as a tuple $M = (T,T_M,V,W_M,E_M,{\cal L})$, such that $T$ and $V$ are, respectively, a time interval and a set of nodes, just like for stream graphs \cite{stream}.
    As for multilayer graphs \cite{mlkiv}, ${\cal L}$ is a set of $d$ {\em aspects}; ${\cal L} = \{L_i\}_{i=1}^d$, and an element $\alpha_i$ of $L_i$ is named {\em elementary layer}. An element of $L=L_1\times \dots \times L_d$ is named {\em layer}.

	$T_M$ is a set of intervals of $T$ so for that each layer $\alpha$, $T_{\alpha}$ is the interval at which the layer exists. For each $t$ in $T$, $\exists \alpha \in L | t \in T_{\alpha}$ (at any time, all the aspects are non-empty).

@@

   $E_M \subseteq T\times V_M \otimes V_M$ are the links appearing with respect to time,  $V_M = \{ (u,\alpha), u\in V, \alpha \in L\}$. The elements of $V_M$ are named {\em node-layer}.

@@

	\subsection{2 examples}
	\begin{ex}[Research world]\label{exresearch}
	We consider a set of people working in research.

@@

	The {\em union} of two substreams $S_1$ and $S_2$ is defined as follows :
	\begin{align*}
		S' = S_1 \cup S_2 = (T', V_1 \cup V_2, W_1 \cup W_2, E' \})\\
		T' = [\min(T_1,T_2),\max(T_1,T_2)]\\
		E' = E_1 \cup E_2 
	\end{align*}

@@

@@

	\begin{prop}
		\[
			\bigcup_{(\alpha,\beta) \in L^2} S^{(\alpha,\beta)} = S_U(M)
		\]
	\end{prop}
	\begin{proof}
		\begin{align*}
			S=\bigcup_{(\alpha,\beta) \in L^2} S^{(\alpha,\beta)}\\
			S=(T^{*},V^{*},W^{*},E^{*})\\
			S_U(M) = (T_U,V_U,W_U,E_U)			
		\end{align*}

	\begin{itemize}
		\item $T=T_U$ by definition of $S_U$. Let's take $t\in T$. By definition of multilayer stream graphs, $\exists \alpha \in L | t\in T_{\alpha}=T^{\alpha,\alpha}$. So $t \in [\underset{(\alpha,\beta) \in L^2}{\min}(T^{\alpha,\beta}),\underset{(\alpha,\beta) \in L^2}{\max}(T^{\alpha,\beta})]=T^{*}$. $T_U \in T^{*}$. 
	Moreover, $\underset{(\alpha,\beta) \in L^2}{\min}(T^{\alpha,\beta}) \geq \min(T)$ 
	and $\underset{(\alpha,\beta) \in L^2}{\max}(T^{\alpha,\beta}) \leq \max(T)$. 
	So $\mathbf{T^{*} = T}$.
		\item  $V_M = V_U$ by definition of $V_U$.$V^{*}=\bigcup_{(\alpha,\beta) \in L^2} V^{\alpha,\beta} \subset V = V_M$.
	Let $(v,\alpha) \in V_U$. So $(v,\alpha) \in V^{\alpha,\alpha} \in V^{*}$.$V^{*}=V_U$.$\mathbf{V^{*}=V_U}$.
		\item $W_U=W_M$ and $W^{*}=\bigcup_{\alpha,\beta \in L^2} W^{\alpha,\beta} \subset W_M$. So as for all $ (t,u,\alpha)$ in $W_M$, $(t,u,\alpha)$ belongs to $W^{\alpha,\alpha}$, $W_M$ is a subset of $W^{*}$. So $\mathbf{W^{*}=W_M}$.
		\item $E_U=E_M$ and $E^{*}=\bigcup_{\alpha,\beta \in L^2}(E^{\alpha,\beta})$ by definition. So as $E^{\alpha,\beta}$ is a subset of $E_M$ for every couple of layers $\alpha,\beta$, $E^{*} \subset E_M$. 
		$\forall e =(t,u,\alpha,v,\beta) \in E_M$, $e \in E^{\alpha,\beta}$. So $\mathbf{E_M=E^{*}}$.
	\end{itemize}		
	\end{proof}
